Characterizing subarctic biomes for land surface modeling of pollution and climate risk

### 2021-04-19 VegOzone.tex
Rewrite contributions

\authorcontribution{SF has written the manuscript, collected and processed ozone and environmental data, and performed all statistical analyses. AVV helped in framing the research article, has performed on-site observation of vegetation damage induced by ozone, advised with regard to plant physiological processes and contributed text to the introduction. LE has contributed to discussions, setup and evaluation of $\mathrm{DO_3SE}$ modeling results, and development of the PDF-based temperature acclimation. CO has collected species or PFT parameters from literature, performed all $\mathrm{DO_3SE}$ simulations and initial graphical checks of the results. ALEB contributed with her experience regarding subarctic vegetation in Finnmark. FS contributed with a summary of the 2018 meteorological conditions. TB gave guidance in a broader research sense. All authors contributed to discussions, writing, and conclusions.} %% this section is mandatory

>>>>

\authorcontribution{SF has written the manuscript, collected and processed ozone and environmental data, and performed all statistical analyses. AVV contributed to framing this research article, has performed the on-site observation of vegetation damage induced by ozone, and advision in plant physiological processes. LE has contributed to framing of the this article, $\mathrm{DO_3SE}$ modeling, and development of the PDF-based temperature acclimation. CO has collected species or PFT parameters from literature, performed all $\mathrm{DO_3SE}$ simulations and initial validation of the results. AE contributed with her experience regarding subarctic vegetation in Finnmark. FS contributed with an assessment of the 2018 meteorological conditions. TB gave guidance in a broader research sense. All authors contributed to discussions, writing, and conclusions.} %% this section is mandatory
